Bridging the Gap Between Visual and Analytical Machine Learning Testing

### 2023-10-25 report/icst24.tex
feat(report): 2023-10-25 Wed 14:22 updates

\begin{IEEEkeywords}
  ML Testing, Visualisations, ???
\end{IEEEkeywords}

@@

Visualisations are used throughout the ML development lifecycle to test various properties of the ML system. In the early stages of the ML development lifecycle, visualisations are extensively used to make sense of the data and verify its statistical properties. During the model development phase, visualisations are used to summarise metrics and contrast different learning algorithms and iteratively fine-tune ML models. Once the model is deployed in production, visualisations are used to continually monitor their performance and trigger a new training cycle once their performance drops below a certain threshold.

Building ML systems is highly iterative and experimental. Information gained from ML visualisations is used to make design and implementation decisions for the following steps of the ML pipeline. For instance, we may visualise the distribution of our training data and find that it is normally distributed. Based on this information, we may opt for a Linear Regression model which assumes normality in the underlying data. However, such expectations regarding the data may be violated once the ML system is deployed in production, where the data constantly changes as a reflect of the real world. Implicit expectations obtained from visualisations must therefore be translated to analytical tests that fail once our expectations regarding the ML system are no longer satisfied.

>>>>

\begin{IEEEkeywords}
  ML Testing, Visualisations, Assertions, Computational Notebooks
\end{IEEEkeywords}

@@

Visualisations are used throughout the ML development lifecycle to test various properties of the ML system. In the early stages of the ML development lifecycle, visualisations are extensively used to make sense of the data and verify its statistical properties. During the model development phase, visualisations are used to summarise metrics and contrast different learning algorithms and iteratively fine-tune ML models. Once the model is deployed in production, visualisations are used to continually monitor their performance and trigger a new training cycle once their performance drops below a certain threshold~\cite{yuan2021survey,hohman2019visual,amershi2015modeltracker,wexler2020if}.

Building ML systems is highly iterative and experimental. Information gained from ML visualisations is used to make design and implementation decisions for the following steps of the ML pipeline. For instance, we may visualise the distribution of our training data and find that it is normally distributed. Based on this information, we may opt for a Linear Regression model which assumes normality in the underlying data. However, such expectations regarding the data may be violated once the ML system is deployed in production, where the data constantly changes as a reflect of the real world~\cite{amershi2019software,sambasivan2021everyone,breck2019data,baylor2017tfx}. Implicit expectations obtained from visualisations must therefore be translated to analytical tests that fail once our expectations regarding the ML system are no longer satisfied.
